comgen-outline

### 2017-06-09 paper/generics-paper.Rmd
comment out latex style figures

\begin{figure*}[t]
\centering
  \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3}
  \caption{
  Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency). 
  Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions. 
  Actual frequency noted on x-axis for examples (left).
  Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions. 
  Error bars suppressed and points jittered on left facet for visual clarity.
  }
  \label{fig:tjScatters}
\end{figure*}

@@

\begin{figure*}[t]
\centering
  \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf}
  \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity).
  Middle: Human endorsements of habitual sentences (Expt. 3b) vs. Predicted log frequency (Expt. 3a), with data for corresponding items from Expt. 2 (assumed to have the same predictive log frequency as baseline). 
  Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).}
  \label{fig:tj3}
  \vspace{-7pt}
\end{figure*}

>>>>

<!-- \begin{figure*}[t] -->
<!-- \centering -->
<!--   \includegraphics[width=0.84\textwidth]{figs/tj-scatters-3} -->
<!--   \caption{ -->
<!--   Human acceptability judgments as a function of the log frequency of action (left) and speaker $S_2$ model predictions (right) for ninety-three unique items (event \textsc{x} frequency).  -->
<!--   Color denotes target-individual frequency of action (log scale), with lighter colors indicating more frequent actions.  -->
<!--   Actual frequency noted on x-axis for examples (left). -->
<!--   Error bars correspond to 95\% bootstrapped confidence intervals for the participant data and 95\% Bayesian credible intervals for the model predictions.  -->
<!--   Error bars suppressed and points jittered on left facet for visual clarity. -->
<!--   } -->
<!--   \label{fig:tjScatters} -->
<!-- \end{figure*} -->

@@

<!-- \begin{figure*}[t] -->
<!-- \centering -->
<!--   \includegraphics[width=\textwidth]{figs/expt3-4-scatters-camera.pdf} -->
<!--   \caption{Left: Predicted log frequency as a function of past log frequency given to the participant (Expt. 3a; CIs suppressed and jitter added for visual clarity). -->
<!--   Middle: Human endorsements of habitual sentences (Expt. 3b) vs. Predicted log frequency (Expt. 3a), with data for corresponding items from Expt. 2 (assumed to have the same predictive log frequency as baseline).  -->
<!--   Right: Endorsements (Expt. 3b) vs. Speaker $S_2$ model predictions using empirically elicited predictive frequencies (Expt. 3a).} -->
<!--   \label{fig:tj3} -->
<!--   \vspace{-7pt} -->
<!-- \end{figure*} -->
